\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}

\usepackage[]{natbib}

\author{Aron Monszpart}
\title{Super-resolution hand-held scanning}
\begin{document}
\maketitle

\begin{abstract}
	ABSTRACT
\end{abstract}

\section{Summary}
	SUMMARY

\tableofcontents

\section{Introduction}
	\begin{itemize}	
		\item Motivation
		\item Overview of approach
		\begin{itemize}
			\item Calibration
			\item Low resolution 3D reconstruction
			\item Pose estimation of new input
			\item Mesh subdivision and 2D projection
			\item Depth upsampling
			\item Mesh enhancement by backprojection
		\end{itemize}
	\end{itemize}

\section{Related work}
	\begin{enumerate}
		\item 3D reconstruction using Multi-view stereo
		\begin{itemize}
			\item Curless and Levoy
			\item Rusinkiewicz
			\item Szeliski
			\item Agarwal
			\item Snavely
			\item Seitz
			\item Furukawa and Ponce
			\item Strecha
			\item etc. from literature review (got good marks for it)
			\item Kim et al: Scene reconstruction from High Spatio-Angular Resolution Light Fields (Siggraph '13)
		\end{itemize}

		\item 3D reconstruction using RGB-D
		\begin{itemize}
			\item Voxelgrid based
			\begin{itemize}
				\item Newcombe: Kinect fusion
				\item Whelan: Kintinuous and other loop closure papers
				\item Vladlen: Dense scene reconstruction with points of interest
				\item etc.
			\end{itemize}

			\item Height-field based, layered
			\begin{itemize}
				\item Adaptive voxelgrid based, scene scale aware (Freiburg)
				\item etc.
			\end{itemize}

			\item Point based
			\begin{itemize}
				\item Damien Lefloch
				\item etc.
			\end{itemize}

			
		\end{itemize}
			
 		\item Pose estimation
		\begin{itemize}
			\item some ICP references
			\item Gyro papers
			\item MVS already earlier
		\end{itemize}
		
		\item Upsampling
		\begin{itemize}
			\item RGB superresolution
			\item Depth superresolution
			\begin{itemize}
				\item Non-guided
				\begin{itemize}
					\item Learning based
						\begin{itemize}
							\item Mac Aodha et al. '12
							\item etc.
						\end{itemize}
					\item Other
					\begin{itemize}
						\item Hornacek et al.: Depth Super Resolution by Rigid Body Self-Similarity in 3D, CVPR '13
						\item etc.
					\end{itemize}
				\end{itemize}
				
				\item Guided
				\begin{itemize}
					\item Joint Bilateral
					\begin{itemize}
						\item Yang '07
						\item etc.
					\end{itemize}
					\item MRF based
					\begin{itemize}
						\item Diebel and Thrun
						\item Schuon et al.
						\item Park et al. '11
						\item Choi et al. '12
						\item Shen and Cheung CVPR '13 (Layer Depth Denoising and Completion for Structured-Light RGB-D Cameras)
						\item etc.
					\end{itemize}
					
					\item Spatio-temporal filtering
					
				\end{itemize}
			\end{itemize}
		\end{itemize}
		
		\item Commercial 3D scanners
		\begin{itemize}
			\item MVS based: Photosynth, Adobe, etc.
			\item Laser scanner systems (industrial)
			\item Kinect based: Scanec, Reva, ReconstructMe, ...
		\end{itemize}
		
		\item Seen/used calibration references
		\item Subdivision references
		\item Efficient raycasting references
		\item (+ Categorize all the ref e-mails from Gabriel, Oisin, Reading groups, etc.)
	
	\end{enumerate}

\include{mysystem}

\section{System plan}
	\begin{itemize}
		\item Calibration
			\begin{itemize}
				\item Depth image based
				\item IR image based
				\item Undistort
			\end{itemize}
		\item Low resolution 3D reconstruction
			\begin{itemize}
				\item Multi View Stereo (VSFM, Bundler, Photosynth, etc.)
				\item Kinect Fusion, PCL::Kinfu
			\end{itemize}
		\item Pose estimation of new input
			\begin{itemize}
				\item VSFM ( for RGB input )
				\item ICP ( for RGB-D input )
				\item Gyro+IMU (a noisy graph of acquired data)
			\end{itemize}
		\item Mesh subdivision (Linear, Butterfly, Catmull-Clark)
		\item 2D projection
			\begin{itemize}
 				\item Raycasting using Octree
				\item GLSL projection
			\end{itemize}
		\item Yang filtering
			\begin{itemize}
				\item Iterative Cross Bilateral filtering
				\item Subpixel accurracy
			\end{itemize}
		\item Mesh enhancement by backprojection
	\end{itemize}
	
\section{System design}
	\begin{itemize}
		\item Implementation details and takeaway experience of "System plan" elements
		\item Merge into previous?
	\end{itemize}
	
\section{Evaluation}
	\begin{itemize}
 	\item Experiments
		\begin{itemize}
			\item Calibration
				\begin{itemize}
					\item Kinect built in calibration
					\item Bogouet calibration with and without lens distortion (PARAMETERS explained)
					\item Undistort effectivity (project undistorted depth map to 3D)
				\end{itemize}
				
			\item Filtering
				\begin{itemize}
					\item CrossBilateral filter vs. Bilateral
					\item Yang vs. CrossBilateral (PARAMETERS explained)
					\item Trilateral, Guided, Pixel Weighted Average Strategy (Garcia et al,ImProc, 2010) - {\bf IF there's time}
				\end{itemize}
			\item Kinect fusion related
			\begin{itemize}
				\item Kinfu vs. Kinfu w/ filtering turned OFF
				\item Kinfu voxel grid resolution ($386^3$,$512^3$,$640^3$)
				\item Kinfu + Yang( original kinect depth frames )
				\item Kinfu + Yang( "arbitrary pose" )
			\end{itemize}
		\end{itemize}
	\item Existing libraries used
	\item Data capturing details
	\item No existing datasets compared (no time)

	\end{itemize}

\section{Results}
\begin{itemize}
	\item Upsampling with original depth frames
	\item Upsampling with simulated "arbitrary pose"
	\item Upsampling with real "arbitrary pose" using VSFM pose est. {\bf IF there's time}
	
	\item So, Yang is is not suitable for this resolution, it only could improve, when the input was much noisier
	\item Different approaches can be plugged in to this framework to enhance depth
\end{itemize}
\section{Conclusions, Future work}
	\begin{itemize}
		\item 3D reconstruction improvements
			\begin{itemize}
				\item Improve on smoothing effect of voxel grid weights
				\item Pose estimation improvements
			\end{itemize}
		\item RGB high-resolution capture, vsfm pose estimation 
		\item Enhancement by best pose selection from input image collection for given pixel/region
	\end{itemize}

\section{References}
	...
	
\cite{Lowe04}

\bibliographystyle{plainnat}
\bibliography{litrev}
	
\end{document}


